% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing
\subsection{Technologies}
\subsubsection{Programming languages}

The system will be coded in Django a high-level Python Web framework, as it is specified in the architecture constraints. Django allows the system to be built in phases, it allows different parts to be programmed and designed then merged at the end of the design. 

\subsubsection{Database technologies}

MySQL will be used to code the database as it is part of the architecture constraints. Also the MySQL database is scalable as it can handle over fifty million rows of data at time. It has a high level of security which allows us to specify which user has privileges, as well as encrypting the passwords of each user. It is cost effective as the University is already running the Novel network on their infrastructure which includes the MySQL database package. 

\subsubsection{Application servers}

The application server chosen will be the Apache server, as it is part of the architecture constraints. The Apache server is already installed on the University's server. Apache server is open source allowing modification if required, it is cost effective due to the nature of being open source, it supports Python which is what the system is to be built on. It is portable allowing it to be installed on any system.

\subsubsection{Testing modules}

The system will be tested using the Django unittest module which comes with the Django package it is part of the architecture constraints. The unittest module allows the sharing and integration of code between seperate tests such as the start up and shutdown of testing. It allows Command-Line interface as well as code imbedded testing. Unittest has functionality to re-use old test code instead of designing the test code over. 

\subsection{Frameworks}
\subsection{Protocols}

\subsubsection{HTTP - HyperText Transfer Protocol}

The system will make use of HTTP to receive requests and send responses through the different access channels. This protocol will define the communication 
between the sytem and web browsers as well the Android application.

\subsubsection{HTTPS - HyperText Transfer Protocol Secure}

The system will make use of HTTPS when communicating sensitive data through the different access channels.

\subsubsection{REST - Representational State Transfer}

Strictly speaking REST is not a protocol, but it makes use of HTTP to provide web services. REST is preferred over SOAP as it is lightweight, easy to use and will provide
better performance in the case of this system. These advantages have made REST the chosen web services protocol. Making use of RESTful web services is an architectural constraint.

\subsubsection{JSON - JavaScript Object Notation}

The system will make use of the JSON protocol to marshal response objects that are requested by other systems. JSON is the preferred
marshaling protocol due to it being efficient and lightweight. When compared to XML, the JSON marshaled objects are smaller in size
and the time taken to process them is less. These performace gains have made JSON the chosen marshaling protocol.

\subsubsection{LDAP - Lightweight Directory Access Protocol}

The system will make use of the LDAP system used by the Department of Computer Science. This system contains the details of the users of the system.
Thus the users will be authenticated through this LDAP system. LDAP is both efficient and low cost. Making use of the LDAP protocol is an architectural constraint. 

\subsection{Libraries}

\subsubsection{JSON Marshaling}

The system will make use of the serialization library provided by Django. The term "serialize" is considered to be synonymous with "marshal" in the Python standard library. Therefore this library is suited for marshaling. This library supports many different formats but specifically supports JSON. This functionality is needed to by the web services.

\subsubsection{LDAP Authentication Integration}

The Django framework provides its own authentication system. To integrate LDAP with the Django framework, 
a new authentication backend must be written and added to the Django framework. This backend must realize the
contract setup by the Django framework. This functionality is needed to authenticate users.

\subsubsection{Importing CSV}

The system will be making use of the django-csv-importer v0.1.3.5 library. This library provides the functionality to transform the data of a CSV file into Django model instance. This functionality is needed to import assessment entries from CSV files.

\subsubsection{Exporting CSV}

The system will be making use of the Python CSV library. This library provides the functionality to data to a CSV file. This functionality is needed to export mark sheets to CSV files.

\subsubsection{Generating PDF's}

The system will be making use of the ReportLab library. This library provides the functionality to dynamically generate reports in the PDF format. This functionality is needed to generate reports requested by the lecturer.