\documentclass[12pt]{article}

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{pdfpages}
\usepackage{lastpage} % Required to determine the last page for the footer
\usepackage{extramarks} % Required for headers and footers
\usepackage{graphicx} % Required to insert images
\usepackage{listings} % Required for insertion of code
\usepackage{courier} % Required for the courier font
\usepackage{hyperref} %hyperlink
\usepackage{float}

% Margins
\topmargin=-0.45in
\evensidemargin=0in
\oddsidemargin=0in
\textwidth=6.5in
\textheight=9.0in
\headsep=0.25in

\linespread{1.1} % Line spacing

\newcommand{\Title}{Design document} % Assignment title
\newcommand{\Class}{Cos\ 301} % Course/class

\begin{document}

	\vspace{4em}
	
	\begin{center}%
	\LARGE \bf \Class: Mini Project phase 2 \\
	  \LARGE \bf \Title \\[4em]
	  \LARGE {\bf Group 8}\\[1em]
	  \LARGE {\bf Group Members:}\\[2em]
	  \large
	     Melany Barnes					(12030466) \\[1em]
	     Zane Bloom						(12236722) \\[1em]
	     Mathys Ellis					(12019837) \\[1em]
	     Zenadia Groenewald				(12265676) \\[1em]
	     Alfred Ngako					(12236731) \\[1em]
	  	 Gerhard Smit					(12282945) \\[1em]
	     {\bf Version 0.5}
	    
	\end{center}
	
	\newpage
		{\LARGE \bf Change Log}\\[2em]
		
		\begin{center}
		\begin{tabular}{|l|p{1.4cm}|p{8cm}|p{2.8cm}|}
		\hline
		\multicolumn{4}{|c|}{\bf Change log} \\
		\hline
		\bf Date & \bf Version & \bf Description & \bf Person \\
		\hline
		11/03/2014 & v 0.0 & Document created & Mathys Ellis \\
		\hline
		11/03/2014 & v 0.1 & Added android application: UI design, Process Specifications and user work flow & Mathys Ellis \\
		\hline
		11/03/2014 & v 0.2 & Some database tables added & Melany Barnes \\
		\hline
		12/03/2014 & v 0.3 & Added android application: API. Modified Process Specifications & Mathys Ellis \\
		\hline
		12/03/2014 & v 0.4 & Added Protocols to be used & Zane Bloom \\
		\hline
		12/03/2014 & v 0.5 & Added Libraries to be used & Zane Bloom \\
		\hline
		%\end{tabbing}
		\end{tabular}
		\end{center}
		
	\newpage
	\tableofcontents
	
	\vspace{0.5in}
	
	\begin{flushleft}
		\LARGE\href{https://github.com/mox1990/COS_301_GROUP8_Phase_2}{GitHub repository: Mini project - Phase 2 -  Group 8}
	\end{flushleft}
	
	\newpage
	\section{Software architecture design}
	
		\vspace{0.2in}
		\input{./subdocs/Software_architecture_design.tex}
		
		
	\section{Application design}
	
		\vspace{0.2in}
		
		
		
	\subsection{Back-end system}

		\vspace{0.2in}
		
		\input{./subdocs/Backend_design.tex}
		
		
	\subsection{Web interface}

	\vspace{0.2in}
	\input{./subdocs/Web_interface.tex}
	
	\newpage
	\subsection{Android application}
			
	\vspace{0.2in}
	\input{./subdocs/Android_app.tex}
	
	
	
	\vspace{0.2in}

	
	\newpage	
	\section{Glossary}
	
		\vspace{0.2in}
		\begin{itemize}
			\item Student - Entailing all students register at the university for specific modules.
			\item Marker - A grouping of including Teaching Assistance and Tutors, which have permission to assign marks.
			\item Lecturer - Co-ordinator and/or module presenter.
			
			\item Markable item - Including tests, class tests, assignments, practicals.
			\item Mark list - List consisting of all students registered for a specific module.
			\item Course - A module presented at the university.
			
			\item Web interface - Browser client.
			\item SSO - Single Sign On.
			\item LDAP - System used during SSO for authentication.
			\item SOAP - Simple Object Access Protocol.
			\item API -	A sub-section of the overall system.
			\item HTTPS - Secured HTTP connection.
			\item HTML 5 - Standardised version of HTML.
			\item PDF -	The format used in statistics exports.
			\item CSV -	Column Separated Values, used for import of marks and student information.
			\item SOAP - Simple Object Access Protocol	
			\item WSDL - Web Service Definition Language
			\item Android - Mobile operating system used.
			\item Django - Web framework used for the systems back-end.
			\item Python - Programming language used in Django.
			\item Java - Used by Android to program application.
			\item MySQL - Language for database structure and queries.
		\end{itemize}	
	
\end{document}
